Overall, we aim for this work to bring a formal IR perspective to the important research area of AUIs while opening new research directions for the application of IR methodology.  As information
retrieval has transformed our web experience, we believe there is
a similar opportunity to transform the present nascent state of AUIs
through optimization and information retrieval principles to make
them more ubiquitous in our daily lives. 

In this paper we have introduced a novel information retrieval perspective of filtering for Adaptive User Interfaces.  In this context, we introduced new filter search algorithms for expected F1-Score based on two different Greedy strategies.  We have also proposed a method for optimization of expected F1-score using a MILP approach for purposes of benchmarking. The evaluations we have performed on a variety of datasets have shown that the Greedy algorithms we have proposed are relatively efficient and provide a good approximation of the optimal MILP solution; Greedy methods may even do better than exact expected F1-score optimization in high noise cases due to their more restricted search space.  Furthermore, we have experimentally demonstrated that the proposed expected F1-Score metric is a good surrogate of the ground truth F1-Score.

% Important areas of future work include enhanced indexing strategies and scalability in filter selection algorithms along with the 
Important areas of future work include consideration of the role of (pseudo-)relevance and other explicit or implicit feedback methods to create a tighter and more responsive user interaction loop.
Furthermore, in combination with user studies and consideration of human factors, future work should also consider novel application-specific objectives, e.g.,  in specific visualization frameworks or based on a ranking theory of results presentation (e.g., using size or color for visual ranking emphasis).  


% For future work, we are currently integrating these algorithms into our existing user interface of graph exploration and mining. We also plan to conduct a user study in the context of natural disasters discussed on twitter to analysis our algorithms and get a real insight of their accuracy. Finally, we plan to investigate new optimization metrics based on visual rendering.